The Application of Magnetic Susceptibility Separation for Measuring Cerebral Oxygenation in Preterm Neonates

### 2024-10-03 index.qmd
fixed spelling errors

For the preceding reasons, non-invasive MRI-based techniques are actively being explored to assess whole-brain oxygenation. MRI based methods have been developed for adults [@jainRapidMagneticResonance2011; @luQuantitativeEvaluationOxygenation2008; @xuNoninvasiveQuantificationWholebrain2009] and are only beginning to be explored in neonates [@devisNoninvasiveMRIMeasurements2014; @liuQuantitativeAssessmentGlobal2014; @qiHemodynamicMetabolicAssessment2018; @jainRapidMagneticResonance2011; @jiangVesselspecificQuantificationNeonatal2019]. One limitation of these methods, however, is the fact that SvO~2~ is often measured using a single slice, averaging values within several voxels in the superior sagitall sinus (SSS). An alternative MRI method using quantiative susceptibility mapping (QSM) has been proposed, which measured SvO~2~ across the whole-brain. However, this method left room for improvement, as it removed the SSS, and required an arbitraty threshold value of 0.15 ppm in order to acquire realistic results [@weberQuantitativeSusceptibilityMapping2021].

In the present study, we set out to determine whether decomposing the QSM image into its paramagnetic and diamagnetic comoponents would allow for a more accurate assessment of SvO~2~ in the central cerebral veins (CCV) of a cohort of preterm neonates. We also had a secondary aim of preserving the SSS vessel in our QSM images and using this data to determine whether a difference in oxygenation existed between the SSS and the CCV.

>>>>

For the preceding reasons, non-invasive MRI-based techniques are actively being explored to assess whole-brain oxygenation. MRI based methods have been developed for adults [@jainRapidMagneticResonance2011; @luQuantitativeEvaluationOxygenation2008; @xuNoninvasiveQuantificationWholebrain2009] and are only beginning to be explored in neonates [@devisNoninvasiveMRIMeasurements2014; @liuQuantitativeAssessmentGlobal2014; @qiHemodynamicMetabolicAssessment2018; @jainRapidMagneticResonance2011; @jiangVesselspecificQuantificationNeonatal2019]. One limitation of these methods, however, is the fact that SvO~2~ is often measured using a single slice, averaging values within several voxels in the superior sagittal sinus (SSS). An alternative MRI method using quantitative susceptibility mapping (QSM) has been proposed, which measured SvO~2~ across the whole-brain. However, this method left room for improvement, as it removed the SSS, and required an arbitrary threshold value of 0.15 ppm in order to acquire realistic results [@weberQuantitativeSusceptibilityMapping2021].

In the present study, we set out to determine whether decomposing the QSM image into its paramagnetic and diamagnetic components would allow for a more accurate assessment of SvO~2~ in the central cerebral veins (CCV) of a cohort of preterm neonates. We also had a secondary aim of preserving the SSS vessel in our QSM images and using this data to determine whether a difference in oxygenation existed between the SSS and the CCV.
